### 2023-02-21 README.Rmd
update doi

# pema: Penalized Meta-Analysis <!--a href='https://osf.io/zcvbs/'><img src='https://github.com/cjvanlissa/pema/raw/master/docs/pema_icon.png' align="right" height="139" /></a-->

[![CRAN status](https://www.r-pkg.org/badges/version/pema)](https://CRAN.R-project.org/package=pema)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://r-pkg.org/pkg/pema)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions)
<!-- [![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions) -->
<!-- [![codecov](https://codecov.io/gh/cjvanlissa/pema/branch/master/graph/badge.svg?token=7S9XKDRT4M)](https://codecov.io/gh/cjvanlissa/pema) -->
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-v2.0%20adopted-ff69b4.svg)](https://www.contributor-covenant.org/version/2/0/code_of_conduct.html)
<!-- [![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969) -->
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->

@@

<!-- ## Where do I start? -->

<!-- For most users, the recommended starting point is to [read the paper](https://osf.io/zcvbs/), currently in press in [Data Science](https://content.iospress.com/journals/data-science/Pre-press/Pre-press), -->
<!-- which introduces the pema workflow, explains the underlying tools, and illustrates how the `pema` package can be used to create a new project that follows the workflow. -->

@@

The `pema` validation paper is currently in preprint stage.
The code and results of the validation study are publicly available.
You can cite `pema` using the following citation (please use the same citation for either the package, or the paper); consider updating that citation once the preprint is published:

> Van Lissa, C. J., & van Erp, S. (2021, December 9). Select relevant moderators using Bayesian regularized meta-regression. Retrieved from psyarxiv.com/6phs5

>>>>

# pema: Penalized Meta-Analysis <!--a href='https://doi.org/10.1002/jrsm.1628'><img src='https://github.com/cjvanlissa/pema/raw/master/docs/pema_icon.png' align="right" height="139" /></a-->

[![CRAN status](https://www.r-pkg.org/badges/version/pema)](https://CRAN.R-project.org/package=pema)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://r-pkg.org/pkg/pema)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions)
<!-- [![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions) -->
<!-- [![codecov](https://codecov.io/gh/cjvanlissa/pema/branch/master/graph/badge.svg?token=7S9XKDRT4M)](https://codecov.io/gh/cjvanlissa/pema) -->
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-v2.0%20adopted-ff69b4.svg)](https://www.contributor-covenant.org/version/2/0/code_of_conduct.html)
<!-- [![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969) -->

@@

## Where do I start?

For most users, the recommended starting point is to [read the paper](https://doi.org/10.1002/jrsm.1628) published in **Research Synthesis Methods**,
which introduces the method, validates it, and provides a tutorial example.

@@

You can cite `pema` using the following citation (please use the same citation for either the package, or the paper):

> Van Lissa, C. J., van Erp, S., & Clapper, E. B. (2023). Selecting relevant moderators with Bayesian regularized meta-regression. *Research Synthesis Methods*. https://doi.org/10.1002/jrsm.1628
